\input{HeadMatter.tex}
	
\begin{flushleft}
\Large\textbf{Assignment 1 (10\% of 40\%)- Microsoft Project}\\
\end{flushleft}

In this assignment you are required to utilise a drawing set to create a fully resourced Microsoft Project Gantt chart, and a cost profile based on the data from the project plan and the Revit Model.  The key deliverables for this project are:

\begin{enumerate}
	\item Fully resourced project plan created in Microsoft Project
	\item Cost accrual model created in Microsoft Excel
\end{enumerate}

\textbf{Scenario}\\


You have been provided with drawings of a simple two story house.  You are to use this design to create a robust project plan for its construction and handover to the client.  You are also required to create a cost accumulation graph for the duration of the build process.  Your costings should include direct \& indirect labour only.  You are not required to include the cost of materials in the project plan.


\vspace{.5cm}

\textbf{Suggested Approach}

\begin{itemize}
	\item Using a deliverable orientated approach (WBS) within Microsoft Project will make the process easier to manage
	\item Keep you approach logical and methodical.  Keep notes of the items you have included in the project plan.
	\item When creating the plan, try to visualise the build process and commit that data to the project plan.
	\item Guesstimates for activity durations are acceptable, but should be reasonable.
	\item Get to know this design; we will be using it again in the next assignment.
	\item Copy your MS Project Resource Usage Data to your Excel Spreadsheet to create daily and daily cumulative totals; this data will enable your cost graph.
\end{itemize}


\textbf{General Scope}

\begin{itemize}
	\item You are required to have at least 70 tasks in the build process, not including summary (roll-up) items
	\item You are required to have at least 20 resources applied to the project
\end{itemize}




\newpage


\textbf{Submission}\\
Your completed assignment comprising all computer files are to be zipped into a single file and uploaded to Microsoft Teams on or before the date and time indicated.  Key components of the submission are:
\begin{itemize}
	\item Microsoft Project File (.mpp)
	\item Revit file, modified as necessary (.rvt)
	\item Excel file (.xlsx)
\end{itemize}




\textbf{Late Submission}\\
Failure to submit your assignment on or before the date and time indicated on Microsoft Teams will result in a penalty of 5\% per day or part thereof.

\vspace{0.5cm}
\textbf{Marking Scheme}

\begin{table}[h!]
     \begin{center}
     \begin{tabular}{p{5cm}  p{5cm} }
     \toprule
      \textbf\large{Element} & \textbf\large{Proportion} \\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}
      \textbf{MS Project Plan } & \textbf{60\%}\\
      \textbf{MS Excel Costing and Graph} & \textbf{40\%}\\
      \\ \bottomrule
      \end{tabular}
      \label{tbl:markSchemeAsmt3}
      \end{center}
 \end{table}


\end{document}