\input{HeadMatter.tex}
	
\begin{flushleft}
\Large\textbf{Assignment 2 (25\% of 50\%)\\
	BIM 360 Checklists: Creation and Use}\\
\end{flushleft}

\textbf{** Please note that the CA component of this module has been increased from 40\% to 50\% as a result of the  COVID-19 measures. **} 

In this assignment you will deploy and use a number of Autodesk BIM360 modules.  A BIM360 project has been setup, and you have full admin access to the project.  The key modules that you will use are:

\begin{enumerate}
	\item BIM360 Model Coordination
	\item BIM360 Field Management
	\item BIM360 Assets 
\end{enumerate}

\textbf{General Scope}\\


You have been provided with a sample check-list produced by the Government of Northern Ireland.  This is a paper based survey and therefore has limitations.  You need to digitise this check-list and create a survey of the Students' Union Building


\textbf{BIM360 Model Coordination}\\



\textbf{BIM360 Field Management}\\



\textbf{BIM360 Assets}\\







\vspace{.5cm}

\textbf{Suggested Approach}

\begin{itemize}
	\item Examine the paper based survey in detail, and determine where improvements can be made using a handheld device approach
	\item Create your checklist template making full use of various question types, required questions, and other attributes.
	\item Test your initial template, and revise as necessary
	\item Complete the live onsite survey, creating issues and markups as necessary
	\item Compile survey data, including all issues and images into a comprehensive report.
\end{itemize}


\newpage


\textbf{Submission}\\
Elements of this project will be completed on BIM360. As such, the submission will be a live document.  All work on the BIM 360 platform must be completed before the date and time specified on MS Teams.  Your completed report is to be uploaded to MS Teams on or before the date and time indicated.  Key components of the submission are:
\begin{itemize}
	\item Completed Survey Template on BIM360
	\item Completed Survey on BIM360	
	\item Completed Survey Report
\end{itemize}




\textbf{Late Submission}\\
Failure to submit your assignment on or before the date and time indicated on MS Teams will result in a penalty of 5\% per day or part thereof.

\vspace{0.5cm}
\textbf{Marking Scheme}

\begin{table}[h!]
     \begin{center}
     \begin{tabular}{p{5cm}  p{5cm} }
     \toprule
      \textbf\large{Element} & \textbf\large{Proportion} \\ 
    \cmidrule(r){1-1}\cmidrule(lr){2-2}
      \textbf{BIM360 Survey Template} & \textbf{40\%}\\
      \textbf{BIM360 Survey Capture} & \textbf{20\%}\\
      \textbf{Report on Survey Findings} & \textbf{40\%}\\
      \\ \bottomrule
      \end{tabular}
      \label{tbl:markSchemeAsmt3}
      \end{center}
 \end{table}


\end{document}